Funding programmes for early career researchers do/not influence their independence

### 2023-08-24 _targets.Rmd
updated pipeline

     # tar_target(sup_path, here::here("data", "raw", "manual_sup_search.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

@@

       # tar_target(sup_path_second, here::here("data", "raw", "manual_sup_search_second.csv"), format = "file"),
      tar_target(sup_control_second, read.csv2(sup_path_second)),
      tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
     tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete)),

>>>>

     # tar_target(sup_path, here::here("data", "raw", "manual_sup_search.csv"), format = "file"),
      tar_target(sup_control, read.csv(sup_path)),

@@

       # tar_target(sup_path_second, here::here("data", "raw", "manual_sup_search_second.csv"), format = "file"),
      tar_target(sup_control_second, read.csv(sup_path_second)),
      tar_target(sup_complete, create_sup_complete(sup_control, sup_control_second, db_path, matching_data)),
     tar_target(ids_complete, create_ids_complete(ids, db_path, matching_data)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete)),

### 2023-08-24 article.Rmd
updated pipeline

### Missing data
```{r echo=FALSE}
d <- tar_read(full_indicator)
d$disc_ford <- substring(d$disc_ford, 0, 1)
d$disc_ford <- as.factor(d$disc_ford)

@@

na_sup <- round((sum(is.na(d$sup_name))/na_counts)*100, 1)
na_pubs <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE))/na_counts)*100, 1)

na_pubs_after <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE) %>% filter(independence_timing == "after_intervention"))/nrow(d %>% filter(!is.na(sup_name)) %>% filter(pub_table_empty == TRUE)))*100, 1)

>>>>

### Missing data
```{r echo=FALSE}
d <- tar_read(full_indicator)
d$disc_ford <- as.factor(d$disc_ford)

@@

na_sup <- round((sum(is.na(d$sup_name))/na_counts)*100, 1)
na_pubs <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)))/na_counts)*100, 1)

na_pubs_after <- round((nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number)) %>% filter(independence_timing == "after_intervention"))/nrow(d %>% filter(!is.na(sup_name)) %>% filter(is.na(pubs_number))))*100, 1)
